---
title: "My Interactive Leaflet Map"
output: html_document
date: "2025-10-08"
---

title: "My Interactive Leaflet Map"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

<style>
  body{
    text-align: justify;
    font-family: sans-serif;
  }
  h1, h2{
    text-align: center;
  }
</style>

# 🗺️ An Interactive Map of Tokyo

This document was created to fulfill the course project requirement. It features an interactive map created with the **Leaflet** package, and the document is automatically dated. The map below displays several famous landmarks in Tokyo, Japan. Click on a marker to see the name of the location!

```{r setup, include=FALSE}
# This chunk handles the setup, including package installation and loading.
# The 'include=FALSE' option means this code will run, but won't appear in the final HTML file.

# --- Package Installation ---
# Note: You only need to run this once. 
# After the first time, you can comment out the install.packages() line to make your document knit faster.
if(!require("leaflet")) install.packages("leaflet")
if(!require("dplyr")) install.packages("dplyr")

# --- Load Libraries ---
library(leaflet)
library(dplyr)
```

## Creating the Interactive Map

```{r create_map, echo=FALSE, message=FALSE, warning=FALSE}
# The 'echo=FALSE' option means the map will be displayed, but the code to create it will be hidden in the webpage.

# 1. Create a data frame of locations in Tokyo
locations_df <- data.frame(
  name = c("Tokyo Tower", "Senso-ji Temple", "Meiji Jingu Shrine", "Shibuya Crossing", "Tokyo Imperial Palace"),
  lat = c(35.6586, 35.7148, 35.6764, 35.6595, 35.6852),
  lng = c(139.7454, 139.7967, 139.6993, 139.7005, 139.7528),
  popup_text = c(
    "<strong>Tokyo Tower</strong><br>A famous communications and observation tower.",
    "<strong>Senso-ji Temple</strong><br>An ancient Buddhist temple, and Tokyo's oldest.",
    "<strong>Meiji Jingu Shrine</strong><br>A Shinto shrine dedicated to Emperor Meiji and his wife.",
    "<strong>Shibuya Crossing</strong><br>One of the busiest intersections in the world.",
    "<strong>Tokyo Imperial Palace</strong><br>The primary residence of the Emperor of Japan."
  )
)

# 2. Create and display the Leaflet map
locations_df %>%
  leaflet() %>%
  addTiles() %>%  # Adds the default OpenStreetMap base tiles
  addMarkers(
    lng = ~lng, 
    lat = ~lat, 
    popup = ~popup_text
  )
```
***
